\documentclass{cse}
% \printanswers

% Exam solution display
\newcommand{\name}{Kevin Lin}
\newcommand{\sid}{1234567890}
\newcommand{\nameleft}{Kevin Lin}
\newcommand{\nameright}{Kevin Lin}

% Course information
\newcommand{\coursenumber}{CSE Course}
\newcommand{\coursetitle}{Course Title}
\newcommand{\offering}{University of Washington, Quarter Year}
\title{Sample Exam}

\begin{document}

\maketitle

This exam has \numquestions{} questions worth a total of \numpoints{} points and is to be completed in 50 minutes.
Two double-sided, 8.5-by-11'' sheets of notes are permitted.
Electronic devices are prohibited.
This exam is preprocessed by a computer when grading, so please \textbf{write darkly and write your answers inside the designated spaces.}

\textbf{Write the statement below in the given blank and sign. You may do this before the exam begins.}

\begin{quote}
    ``I have neither given nor received any assistance in the taking of this exam.''
\end{quote}

\fillin[I have neither given nor received any assistance in the taking of this exam.][\textwidth]

\begin{flushright}
    Signature: \fillin[\name][2in]
\end{flushright}

\medskip

\begin{minipage}[t]{2.25in}
\gradetablestretch{1.265}
\vtword{\textbf{Total}}
\begin{center}
\pointtable[v][questions]
\end{center}
\end{minipage}%
\begin{minipage}[t]{3.75in}
\renewcommand{\arraystretch}{2.235}
\begin{tabularx}{\textwidth}{|X|m{2in - 2\tabcolsep}|}
\hline
Name & \solinline{\name} \\
\hline
Student ID & \solinline{\sid} \\
\hline
Name of person to left & \solinline{\nameleft} \\
\hline
Name of person to right & \solinline{\nameright} \\
\hline
\end{tabularx}
\end{minipage}

\medskip

\begin{itemize}[itemsep=0pt]
\item Take notes in any white space. \textbf{Only answers written in the designated spaces will be graded.}
\item \mcqb{} indicates that only one circle may be chosen. Fill-in the shape completely: \mcqs{}.
\item \moqb{}\, indicates that more than one box may be selected. Fill-in the shape completely: \moqs{}.
\item Work through the problems you are comfortable with first.
\item Not all information provided in a problem may be useful.
\item Unless we specifically give you the option, the correct answer is not, `does not compile.'
\end{itemize}

\clearpage

\begin{questions}
\question[1] \questiontitle{Hello, world!}
\end{questions}

\end{document}
